literature coding explore

### 2024-06-03 reports/lit_codes_explore.qmd
sankey plot

library(tidyverse)
library(tidyquant)
library(here)
library(kableExtra)
library(waffle)
library(extrafont)
library(hrbrthemes)
library(patchwork)

@@

>>>>

library(tidyverse)
library(tidyquant)
library(here)
library(kableExtra)
library(waffle)
library(extrafont)
library(hrbrthemes)
library(patchwork)
library(ggalluvial)
library(ggrepel)
library(forcats)

@@

### Sankey diagram of code heirarchies 
Here, each of the codes and their subcodes are presented. The presented percentages represent totals across all codes.

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 15
#| fig-height: 10

sankey_df <- read.csv(here("data/sankey_freq.csv"))

sankey_df$code_cat <- factor(sankey_df$code_cat, levels = c("Data barrier", "Ecological barrier", "Social barrier", "Data bridge", "Ecological bridge", "Social bridge"))

sankey_df <- sankey_df %>%
mutate(sum_codes = sum(total), 
      perc_codes = (total/sum_codes)*100, 
      round_perc = round(perc_codes, 0))

ggplot(data = sankey_df,
       aes(axis1 = fct_reorder(bridge_barr, -perc_codes), axis2 = fct_reorder(code_cat, -perc_codes), axis3 = fct_reorder(code_name, -perc_codes), y = perc_codes)) +
  geom_alluvium(aes(fill = code_cat, color = code_cat), size = 1.5, alpha = 0.8, width = 0.05) +
  geom_stratum(size = 1.5, color = "grey60", 
              width = c(1/12,1/12,1/3,1/3,1/3,1/3,1/3,1/3,1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18)) +
  geom_text(stat = "stratum", 
    aes(label = after_stat(stratum)),
    angle = c(90,90,0,0,0,0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    size = c(7,7,5,5,5,5,5,5,3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3,   3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3), 
    nudge_y = c(0,0,0,0,0,0,0,0,0, #poor communication and outreach
                0.5, #model abuse
                1, #lack of political permanance
                1.5, #indirect socioeconomic consequences
                1.8, #target species is a prey specialist
                2, #resource availability
                2, #climate change adding uncertainty
                2, #data transparency
                2, #need for multi-species management
                2, #distinct habitat preference
                2, #fine scale management
                1.5, #management scale system needs
                2, #management scale aligns
                0.8, #feasibility
                0,0,0,0,0,0,0,0,0,0,0,0,0,0, 0), 
    nudge_x = c(-0.01,-0.01,0,0,0,0,0,0,0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05,   0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05), 
    hjust = c(0.5, 0.5, 0.5,0.5,0.5,0.5,0.5,0.5,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)) +

  xlim(0.89, 3.6) +
  ylim(-1, 100)+
  labs(y = "Percent of all codes (%)", x = "") +
  theme_minimal()+
  theme(axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16), 
        legend.position = "none", 
        axis.text.x = element_blank(), 
        panel.grid.major = element_blank())+
  scale_fill_manual(values = c("#F48136", "#F46036", "#F44336", "#CFE2F3", "#C5E0B4", "#45818E"))+
  scale_color_manual(values = c("#F48136", "#F46036", "#F44336", "#CFE2F3", "#C5E0B4", "#45818E"))
